taxize - taxonomic search and retrieval in R

### 2013-05-28 inst/doc/taxize_withcode.tex

% \usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\usepackage{natbib}
% \usepackage[english]{babel}
\usepackage{footnote}
\hypersetup
{
  colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{## From CRAN}
\hlfunctioncall{install.packages}(\hlstring{"taxize"})
\end{alltt}
\begin{verbatim}

The downloaded binary packages are in
	/var/folders/kv/rpbb_gw965l0lhrq8w92n8j40000gn/T//Rtmp44FcYx/downloaded_packages
\end{verbatim}
\begin{alltt}

\hlcomment{## From GitHub}
\hlfunctioncall{install.packages}(\hlstring{"devtools"})
\end{alltt}
\begin{verbatim}

The downloaded binary packages are in
	/var/folders/kv/rpbb_gw965l0lhrq8w92n8j40000gn/T//Rtmp44FcYx/downloaded_packages
\end{verbatim}
\begin{alltt}
\hlfunctioncall{require}(devtools)
\hlfunctioncall{install_github}(\hlstring{"taxize_"}, \hlstring{"ropensci"})
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\hlcomment{# Let's take a peek at the data, excluding the data source ID and score}
\hlcomment{# columns}
temp[, -\hlfunctioncall{c}(1, 4)]
\end{alltt}
\begin{verbatim}
    submitted_name                 name_string                   title
1 Helianthos annus        Helianthus annuus L.       Catalogue of Life
3 Helianthos annus            Helianthus annus GBIF Taxonomic Backbone
4 Helianthos annus            Helianthus annus                     EOL
5 Helianthos annus         Helianthus annus L.                     EOL
6 Helianthos annus            Helianthus annus           uBio NameBank
2    Homo saapiens Homo sapiens Linnaeus, 1758       Catalogue of Life
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# Using ITIS}
\hlfunctioncall{tax_name}(query = \hlstring{"Helianthus annuus"}, get = \hlstring{"family"}, db = \hlstring{"itis"})
\end{alltt}
\begin{verbatim}

Retrieving data for species ' Helianthus annuus '
[1] "Asteraceae"
\end{verbatim}
\begin{alltt}

\hlcomment{# Using NCBI}
\hlfunctioncall{tax_name}(query = \hlstring{"Helianthus annuus"}, get = \hlstring{"family"}, db = \hlstring{"ncbi"})
\end{alltt}
\begin{verbatim}

Retrieving data for species ' Helianthus annuus '
[1] "Asteraceae"
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# In this example, this search term has many matches. The function returns}
\hlcomment{# a data.frame of the matches, and asks for user input. Enter the row}
\hlcomment{# number of the name you want.}
\hlfunctioncall{get_tsn}(searchterm = \hlstring{"Elisabethae"}, searchtype = \hlstring{"sciname"})
\end{alltt}
\begin{verbatim}

Retrieving data for species ' Elisabethae '

                           combinedname    tsn
1                  Bittacus elisabethae 810495
2            Caenaugochlora elisabethae 754498
3                  Ceratina elisabethae 765455
4            Dolicheremaeus elisabethae 740429
5                  Euphione elisabethae  64893
6                 Harmothoe elisabethae 573734
7                  Hydraena elisabethae 815669
8                    Lizzia elisabethae  48875
9                   Melinna elisabethae  67765
10            Myrmicocrypta elisabethae 580527
11           Myzomela boiei elisabethae 713955
12             Notosacantha elisabethae 838430
13               Odontomyia elisabethae 627043
14             Parabelbella elisabethae 737749
15                Peltigera elisabethae 191230
16          Polymorphanisus elisabethae 600292
17        Pseudopterogorgia elisabethae  52264
18                  Rhantus elisabethae 815107
19              Scyllarides elisabethae 553004
20       Sellnickochthonius elisabethae 735137
21       Serilophus lunatus elisabethae 711636
22                Stenhelia elisabethae  87927
23              Tetramorium elisabethae 582397
24                Theridion elisabethae 868794
25             Trichoniscus elisabethae 597365
26 Trichoniscus elisabethae estoniensis 598124

More than one TSN found for species ' Elisabethae '!

          Enter rownumber of species (other inputs will return 'NA'):

Returned 'NA'!
 1 
NA 
attr(,"class")
[1] "tsn"
\end{verbatim}
\begin{alltt}

\hlcomment{# You can pass in a long list of taxonomic names}
splist <- \hlfunctioncall{c}(\hlstring{"annona cherimola"}, \hlstring{"annona muricata"}, \hlstring{"quercus robur"}, \hlstring{"shorea robusta"}, 
    \hlstring{"pandanus patina"}, \hlstring{"oryza sativa"}, \hlstring{"durio zibethinus"})
\hlfunctioncall{get_tsn}(searchterm = splist, searchtype = \hlstring{"sciname"})
\end{alltt}
\begin{verbatim}

Retrieving data for species ' annona cherimola '

Retrieving data for species ' annona muricata '

Retrieving data for species ' quercus robur '

Retrieving data for species ' shorea robusta '

Retrieving data for species ' pandanus patina '

Retrieving data for species ' oryza sativa '

Retrieving data for species ' durio zibethinus '
[1] "506198" "18098"  "19405"  "506787" "507376" "41976"  "506099"
attr(,"class")
[1] "tsn"
\end{verbatim}
\begin{alltt}

\hlcomment{# In this example, note that no match at all returns an NA}
\hlfunctioncall{get_uid}(sciname = \hlfunctioncall{c}(\hlstring{"Chironomus riparius"}, \hlstring{"aaa vva"}))
\end{alltt}
\begin{verbatim}

Retrieving data for species ' Chironomus riparius '

Retrieving data for species ' aaa vva '
[1] "315576" NA      
attr(,"class")
[1] "uid"
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\hlcomment{# Fetch the tree - the formatting of names and higher taxonmy is done}
\hlcomment{# within the function}
tree <- \hlfunctioncall{phylomatic_tree}(taxa = taxa, get = \hlstring{"POST"}, informat = \hlstring{"newick"}, method = \hlstring{"phylomatic"}, 
    storedtree = \hlstring{"R20120829"}, taxaformat = \hlstring{"slashpath"}, outformat = \hlstring{"newick"}, 
    clean = \hlstring{"true"})
\end{alltt}
\begin{verbatim}

Retrieving data for species ' Poa annua '

Retrieving data for species ' Abies procera '

Retrieving data for species ' Helianthus annuus '
\end{verbatim}
\begin{alltt}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
ia <- \hlfunctioncall{iucn_summary}(\hlfunctioncall{c}(\hlstring{"Panthera uncia"}, \hlstring{"Lynx lynx"}))
\hlfunctioncall{iucn_status}(ia)
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\bibliography{refs}

>>>>

% \usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\usepackage{natbib}
% \usepackage[english]{babel}
\usepackage{footnote}
\hypersetup
{
  colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{## From CRAN}
\hlfunctioncall{install.packages}(\hlstring{"taxize"})

\hlcomment{## From GitHub}
\hlfunctioncall{install.packages}(\hlstring{"devtools"})
\hlfunctioncall{require}(devtools)
\hlfunctioncall{install_github}(\hlstring{"taxize_"}, \hlstring{"ropensci"})
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\hlcomment{# Let's take a peek at the data, excluding the data source ID and score}
\hlcomment{# columns}
temp[, -\hlfunctioncall{c}(1, 4)]
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# Using ITIS}
\hlfunctioncall{tax_name}(query = \hlstring{"Helianthus annuus"}, get = \hlstring{"family"}, db = \hlstring{"itis"})
\end{alltt}
\begin{verbatim}
      family
1 Asteraceae
\end{verbatim}
\begin{alltt}

\hlcomment{# Using NCBI}
\hlfunctioncall{tax_name}(query = \hlstring{"Helianthus annuus"}, get = \hlstring{"family"}, db = \hlstring{"ncbi"})
\end{alltt}
\begin{verbatim}
      family
1 Asteraceae
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# In this example, this search term has many matches. The function returns}
\hlcomment{# a data.frame of the matches, and asks for user input. Enter the row}
\hlcomment{# number of the name you want.}
\hlfunctioncall{get_tsn}(searchterm = \hlstring{"Elisabethae"}, searchtype = \hlstring{"sciname"})
\end{alltt}
\begin{verbatim}
                           combinedname    tsn
1                  Bittacus elisabethae 810495
2            Caenaugochlora elisabethae 754498
3                  Ceratina elisabethae 765455
4            Dolicheremaeus elisabethae 740429
5                  Euphione elisabethae  64893
6                 Harmothoe elisabethae 573734
7                  Hydraena elisabethae 815669
8                    Lizzia elisabethae  48875
9                   Melinna elisabethae  67765
10            Myrmicocrypta elisabethae 580527
11           Myzomela boiei elisabethae 713955
12             Notosacantha elisabethae 838430
13               Odontomyia elisabethae 627043
14             Parabelbella elisabethae 737749
15                Peltigera elisabethae 191230
16          Polymorphanisus elisabethae 600292
17        Pseudopterogorgia elisabethae  52264
18                  Rhantus elisabethae 815107
19              Scyllarides elisabethae 553004
20       Sellnickochthonius elisabethae 735137
21       Serilophus lunatus elisabethae 711636
22                Stenhelia elisabethae  87927
23              Tetramorium elisabethae 582397
24                Theridion elisabethae 868794
25             Trichoniscus elisabethae 597365
26 Trichoniscus elisabethae estoniensis 598124
 1 
NA 
attr(,"class")
[1] "tsn"
\end{verbatim}
\begin{alltt}

\hlcomment{# You can pass in a long list of taxonomic names}
splist <- \hlfunctioncall{c}(\hlstring{"annona cherimola"}, \hlstring{"annona muricata"}, \hlstring{"quercus robur"}, \hlstring{"shorea robusta"}, 
    \hlstring{"pandanus patina"}, \hlstring{"oryza sativa"}, \hlstring{"durio zibethinus"})
\hlfunctioncall{get_tsn}(searchterm = splist, searchtype = \hlstring{"sciname"})
\end{alltt}
\begin{verbatim}
[1] "506198" "18098"  "19405"  "506787" "507376" "41976"  "506099"
attr(,"class")
[1] "tsn"
\end{verbatim}
\begin{alltt}

\hlcomment{# In this example, note that no match at all returns an NA}
\hlfunctioncall{get_uid}(sciname = \hlfunctioncall{c}(\hlstring{"Chironomus riparius"}, \hlstring{"aaa vva"}))
\end{alltt}
\begin{verbatim}
[1] "315576" NA      
attr(,"class")
[1] "uid"
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\hlcomment{# Fetch the tree - the formatting of names and higher taxonmy is done}
\hlcomment{# within the function}
tree <- \hlfunctioncall{phylomatic_tree}(taxa = taxa, get = \hlstring{"POST"}, informat = \hlstring{"newick"}, method = \hlstring{"phylomatic"}, 
    storedtree = \hlstring{"R20120829"}, taxaformat = \hlstring{"slashpath"}, outformat = \hlstring{"newick"}, 
    clean = \hlstring{"true"})

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
ia <- \hlfunctioncall{iucn_summary}(\hlfunctioncall{c}(\hlstring{"Panthera uncia"}, \hlstring{"Lynx lynx"}))
\hlfunctioncall{iucn_status}(ia)
\end{alltt}
\begin{verbatim}
Panthera uncia      Lynx lynx 
          "EN"           "LC" 
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\bibliographystyle{eco_lett}
\bibliography{refs}
